\textit{Admiral Radar: Space Expedition}  allows players to enjoy the gameplay mechanics originally found in \textit{Captain Sonar} but without the need for players to be in the same geographic location. \textit{Captain Sonar} along with many other board games don?t have as much of a chance to shine in the spotlight due its eclipsing in popularity from video games. A game like this has huge entertainment potential if properly ported to a more complex, convenient and popular platform, specifically on the computer. The enhanced complexity of the computer platform can allow for this game?s shortcomings to be eliminated ? and that is what this project aims to do.

There has been significant prior work in this area in the form of efforts to computerize various board games. The most familiar example of such work may be the video and computer game versions of the board game Monopoly. The experience provided by such app is generally high-quality, however is limited to that specific game. More complicated, less universally known games are less frequently converted into applications. We intend to develop our game on a more user friendly GUI and implement all the benefits associated with digitization.

\textit{Captain Sonar} is a board game released in 2016 that provides an engaging mechanic for team building and cooperative play. In the game, players form teams of up to four and assume various roles onboard a submarine. The captain steers the submarine, the radio officer determines the location of an enemy submarine, the first mate ensures that sensors and weapons will be ready to be used, and the engineer fixes broken systems. Each movement of the submarine is accompanied by actions from each team member, which together comprise one game turn. Turns for each team may occur at different rates - in other words, each team?s turn is not dependent on the others?. Such a game structure, called a ?real time? board game, is uniquely fun and engaging while an exceptional promoter for teamwork. Thus, our project will use the mechanics and rules from \textit{Captain Sonar} while using a space-based backstory and visual theme.