\subsection*{Functional Requirements}

\hspace*{6mm} User Stories to be implemented in this sprint are shown in \textit{italitcs}. 

\subsubsection*{General}
\begin{enumerate}[leftmargin=\listmargin]
\item \textit{As a user, I would like to be able to login using an id and password.}
\item As a user, I would like to be able to have an avatar and customize my profile
\item \textit{As a user, I would like to be able to start, join, and end a game when I like.}
\item As a user, I would like to be able to select a team and position on my team
\item As a user, I would like to be able to select a map from variety of maps
\item \textit{As a user, I would like to be able to play on a turn based mode}
\item As a user, I would like to be able to have a second mode of playing: real-time
\item As a user, I would like to be able to text chat with my teammates in-game
\item As a user, I would like to be able to perform the actions required for a spacewalk
\item As a user, I would like to be able to play the game entirely online, without a desktop client
\item As a user, I would like to be able to play with less than four players by having the computer take over a role
\end{enumerate}
\subsubsection*{Captain}
\begin{enumerate}[resume, leftmargin=\listmargin]
\item As a user, I would like to be able to send directions to navigate the spaceship
\item As a user, I would like to be able to know when a special ship system is ready 
\item As a user, I would like to be able to fire a rocket, drone, the radar, or mines.
\item As a user, I would like to be able to deploy the ship's boosters.
\item As a user, I would like to be able to fire a remotely-detonated mine.
\item As a user, I would like to be able to know when a system is disabled
\item As a user, I would like to be able to get information about the enemy spaceships supposed position from the radio operator
\item As a user, I would like to be able to begin a spacewalk.
\item As a user, I would like to be able to see where my team has laid mines
\end{enumerate}
\subsubsection*{First Mate}
\begin{enumerate}[resume, leftmargin=\listmargin]
\item As a user, I would like to be able to charge a system on every move
\item As a user, I would like to be able to deploy the Sonar or a Drone.
\item As a user, I would like to be able to monitor the total health of the ship
\end{enumerate}
\subsubsection*{Engineer}
\begin{enumerate}[resume, leftmargin=\listmargin]
\item As a user, I would like to be able to keep track of which systems are disabled and which get repaired
\item As a user, I would like to ask the captain to follow a certain course to repair a system
\item As a user, I would like to select a component to be disabled after a movement.
\end{enumerate}
\subsubsection*{Radio Operator}
\begin{enumerate}[resume, leftmargin=\listmargin]
\item As a user, I would like to be able to get the courses of enemy spaceships
\item As a user, I would like to be able to click on different areas and plot supposed paths
\item As a user, I would like to be able to keep tracks of mines, both ours and enemies
\item As a user, I would like to be able to advise captain on when to deploy mine
\item As a user, I would like to be able to keep track of disclosed locations of enemy
\item As a user, I would like to be able to adjust predicted enemy courses based on information received
\end{enumerate}
\subsubsection*{Developer}
\begin{enumerate}[resume, leftmargin=\listmargin]
\item As a developer, I would like to be able to make a separate server (REMOVED FOR REDUNDANCY)
\item \textit{As a developer, I would like to be able to store game information in the server}
\item \textit{As a developer, I would like to be able to communicate between the server and client}
\item \textit{As a developer, I would like to be able to have a database for user profile}
\item As a developer, I would like to be able to have accommodation for real-time play
\end{enumerate}
\subsection*{Non-Functional Requirements}
\begin{enumerate}[resume, leftmargin=\listmargin]
\item As a Player, I would like to keep GUI input delays low.
\item As a Player, I would like all communications (text chat, notifications, etc.) between clients and the server to have low latency, especially in real-time mode, for enjoyable gameplay.
\item As a Player I would like the audio feedback to be synced with the visuals.
\item \textit{As a Developer, I would like the server to receive all inputs from each of 4 clients before executing the team's move.}
\item As a Developer, I would like each team's clients to only receive information that they are entitled to know. (e.g. they should not receive the other team's location)
\item \textit{As a Developer, I would like each player's client to be distinct and separate. No player role should be able to perform actions of other team members for them.}
\item As a Player or Developer, I would like the game to be capable of handling more than 2 teams (8 players) (if time allows).
\item \textit{As a Player or Developer, I would like communications with the login server to be encrypted and secure. Each player should only be able to access their own account.}
\item \textit{As a user, I would like to interact with the game using a Graphical Interface. (NEW USER STORY)}
\end{enumerate}
