In this sprint we intend to build the very basic functionality of the game. On the server side, this will include the relational database structure and the interface software inside the Java server to connect to it. On the client side, we will implement the graphical user interface in a basic fashion, without many of the advanced graphics and user experience additions that will be present in the final version. The backend side of the interface will allow control of the GUI in a way that allows us to test functionality, but does not necessarily allow full playability of the game. Finally, the backend of the client will be able to connect to the basic server and interface with the login features.\\

\textbf{SCRUM Master:} Sam Buck\\


\textbf{SCRUM Meetings} Monday and Thursday, 8pm\\

\noindent There are several risks or challenges which we foresee in this sprint. The most obvious are technical: ensuring the git works with all users' development environments, that the server implementation properly interacts with the database software, and that we're able to properly use all APIs which the project requires. Coordinating the user interface and the backend could also be challenging, as the MVC paradigm we've designed the client under expects the controller classes to interact properly with several different aspects of the code, each written by different members. The final significant task is interpersonal: while our team has come together as a working unit, we have not yet worked on writing software together, and may face issues when attempting to work together when writing integrated software.